---
title: "weekday_weekend_10"
author: "Min Hyung Lee"
date: "2017년 5월 24일"
output: html_document
---

## Data Preprocessing about Survey

```{r phq9 survey}
setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/survey")

phq9 <- read.csv("PHQ-9.csv", stringsAsFactors = FALSE)

str(phq9)

phq9_ans <- subset(phq9, select = -Response)

## Q&A <- give weight the answer

## Not at all : 0
## several days : 1
## More than half the days : 2
## Nearly every day : 4

colnames(phq9_ans) <- c("uid", "type", "Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8", "Q9")
phq9_ans[phq9_ans == "Not at all"] <- 0
phq9_ans[phq9_ans == "Several days"] <- 1
phq9_ans[phq9_ans == "More than half the days"] <- 2
phq9_ans[phq9_ans == "Nearly every day"] <- 4

phq9_ans[phq9_ans == "pre"] <- "Baseline"
phq9_ans[phq9_ans == "post"] <- "Follow_up"

phq9_ans$Q1 <- as.numeric(phq9_ans$Q1)
phq9_ans$Q2 <- as.numeric(phq9_ans$Q2)
phq9_ans$Q3 <- as.numeric(phq9_ans$Q3)
phq9_ans$Q4 <- as.numeric(phq9_ans$Q4)
phq9_ans$Q5 <- as.numeric(phq9_ans$Q5)
phq9_ans$Q6 <- as.numeric(phq9_ans$Q6)
phq9_ans$Q7 <- as.numeric(phq9_ans$Q7)
phq9_ans$Q8 <- as.numeric(phq9_ans$Q8)
phq9_ans$Q9 <- as.numeric(phq9_ans$Q9)

phq9_ans$type <- as.factor(phq9_ans$type)

phq9_ans$sum <- rowSums(phq9_ans[,3:11])

phq9_ans_split <- split(phq9_ans, phq9_ans$type)

phq9_ans_baseline <- phq9_ans_split$Baseline[c(1,12)]
phq9_ans_followup <- phq9_ans_split$Follow_up[c(1,12)]

phq9_ans_change <- merge(x = phq9_ans_followup, y = phq9_ans_baseline, by ="uid")

phq9_ans_change$minus <- phq9_ans_change$sum.x - phq9_ans_change$sum.y
phq9_ans_change <- phq9_ans_change[c(1, 4)]



```

# A graph about PHQ-9 Survey.

```{r Figure_1}

library(ggplot2)

figure_1_A <- ggplot(phq9_ans_baseline, aes(x=sum)) + geom_bar(fill="dark blue") +coord_flip()
figure_1_A + xlab("Number of Subjects") + ylab("PHQ-9 Score") + ggtitle("Baseline")
# Figure 1. A

figure_1_B <- ggplot(phq9_ans, aes(x=type, y=sum, group=uid)) + geom_point() + geom_line()
figure_1_B + ylab("PHQ-9 Score") + ggtitle("Change")
# Figure 1. B

figure_1_C <- ggplot(phq9_ans_followup, aes(x=sum)) + geom_bar(fill="dark blue") +coord_flip()
figure_1_C + xlab("Number of Subjects") + ylab("PHQ-9 Score") + ggtitle("Follow-up")
# Figure 1. C

```

# 1. Weekday

```{r features_Location Variance, message=FALSE, warning=FALSE}
getwd()
setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekday")

library(readr)

gps_dir <- c("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekday")
gps_file <- list.files(gps_dir)
gps_file_count <- length(gps_file)

# import dataset, gps sensing file
for(i in 1:gps_file_count){
    oname <- substr(gps_file[i], 1,13)
    assign(oname, read_csv(paste(gps_dir,"/", gps_file[i], sep = "")))
}

# Location Variance calculate function
location_variance <- function(x){
    latitude_var = var(x$latitude, na.rm = T)
    longitude_var = var(x$longitude, na.rm = T)
    location_variance = log10(latitude_var + longitude_var)
    return(location_variance)
}

features_10weekday_all <- data.frame()

# feature_10week_all <- features data set

for(i in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[i], sep = ""))
    cc <-location_variance(df)
    features_10weekday_all <- rbind(features_10weekday_all, c(cc))
}

names(features_10weekday_all) <- c("LocationVariance")

################################################################################

uid <- substr(list.files(gps_dir), 11, 13)
uid <- as.data.frame(uid)
features_10weekday_all <- cbind(features_10weekday_all, uid)
features_10weekday_all <- features_10weekday_all[,c(2,1)]

# cbind the "uid" to features_10weekday_all dataset.

################################################################################

## Speed Mean, Speed Variance, Total Distance calculate.
user_speed <- data.frame()

for(j in 1:gps_file_count){
    x <- read_csv(paste(gps_dir,"/", gps_file[j], sep = ""))
    k <- nrow(x) - 1
    
    u00_stat <- data.frame()
    
    for(i in 2:k){
        v = sqrt(((x[[i,5]]-x[[i-1,5]]) / (x[[i,1]] - x[[i-1,1]]))^2 + ((x[[i,6]]-x[[i-1,6]]) / (x[[i,1]] - x[[i-1,1]]))^2)
        
        distance = sqrt((x[[i,5]]-x[[i-1,5]])^2 + (x[[i,6]]-x[[i-1,6]])^2)
        
        u00_stat <- rbind(u00_stat, c(v, distance))
    }
    colnames(u00_stat) <- c("V", "distance")
    user_speed <- rbind(user_speed, c(mean(u00_stat$V), var(u00_stat$V), sum(u00_stat$distance)))
}



features_10weekday_all <- cbind(features_10weekday_all, user_speed)

names(features_10weekday_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance")


```

```{r clustering and features about Number of Clusters, message=FALSE, warning=FALSE}

# Number of location clusters found by the adaptive k-means algorithm
install.packages("akmeans", repos="http://cran.rstudio.com/")
library(akmeans)

set.seed(212)

num_cluster <- function(x){
    n_stationary <- subset(x, travelstate == "stationary")
    set.seed(212)
    adaptive_kmeans <- akmeans(n_stationary[,c("latitude", "longitude")],ths1 = 0.00005, min.k =1, max.k = 100)
    return(nrow(adaptive_kmeans$centers))
}


numberCluster <- data.frame()


for(i in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[i], sep = ""))
    cc <- num_cluster(df)
    numberCluster <- rbind(numberCluster, cc)
}

features_10weekday_all <- cbind(features_10weekday_all, numberCluster)

names(features_10weekday_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters")


```

### Feature_Cluster_entropy calculate code
```{r features about Entropy, message=FALSE, warning=FALSE}


cluster_entropy <- function(x){
    x_stationary <- subset(x, travelstate == "stationary")
    set.seed(212)
    adaptive_kmeans <- akmeans(x_stationary[,c("latitude", "longitude")],ths1 = 0.00005, min.k =1, max.k = 10)
    return(adaptive_kmeans$size)
}

Entropy <- data.frame()

for(j in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[j], sep = ""))
    aa <- cluster_entropy(df)
    aa <- prop.table(aa)
    
    k <- features_10weekday_all[[j,6]]
    x = 0
    for(i in 1:k){
        hap <- aa[i] * log(aa[i])
        x = x + hap
    }
    
    Entropy <- rbind(Entropy, -x)
}

features_10weekday_all <- cbind(features_10weekday_all, Entropy)

names(features_10weekday_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters", "Entropy")

```

### Feature_Normalized Entropy calculate code
```{r Normalized Entropy}

norm_entropy = features_10weekday_all$Entropy / log(features_10weekday_all$NumberofClusters)

norm_entropy <- as.data.frame(norm_entropy)
norm_entropy$norm_entropy[is.na(norm_entropy$norm_entropy)] <- 0

features_10weekday_all <- cbind(features_10weekday_all, norm_entropy)

names(features_10weekday_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters", "Entropy", "NormalizedEntropy")


```

### Feature_Home Stay calculate code
Actually, it is difficult to definite home cluster. so i just determined that the biggest size of cluster is home cluster. so, there will be a little mistake with real home cluster.

```{r features about Home Stay, message=FALSE, warning=FALSE}
homestay <- function(x){
    set.seed(212)
    adaptive_kmeans <- akmeans(x[,c("latitude", "longitude")],ths1 = 0.00005, min.k=1)
    return(adaptive_kmeans$size)
}

Homestay <- data.frame()

for(i in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[i], sep = ""))
    aa <- cluster_entropy(df)
    aa <- prop.table(aa)
    
    home_sort <- sort(aa, decreasing = TRUE)[1]
    
    Homestay <- rbind(Homestay, home_sort)
}

features_10weekday_all <- cbind(features_10weekday_all, Homestay)

names(features_10weekday_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters", "Entropy", "NormalizedEntropy", "HomeStay")

```


```{r}

####################### 완성된 featurers를 통한 분석 비교 #######################


analysis_10weekday_baseline <- merge(x = features_10weekday_all, y = phq9_ans_baseline, by ="uid")
analysis_10weekday_followup <- merge(x = features_10weekday_all, y = phq9_ans_followup, by ="uid")
analysis_10weekday_change <- merge(x = features_10weekday_all, y = phq9_ans_change, by ="uid")


aa <- cor.test(analysis_10weekday_baseline$LocationVariance, analysis_10weekday_baseline$sum)
ab <- cor.test(analysis_10weekday_baseline$SpeedMean, analysis_10weekday_baseline$sum)
ac <- cor.test(analysis_10weekday_baseline$SpeedVariance, analysis_10weekday_baseline$sum)
ad <- cor.test(analysis_10weekday_baseline$TotalDistance, analysis_10weekday_baseline$sum)
ae <- cor.test(analysis_10weekday_baseline$NumberofClusters, analysis_10weekday_baseline$sum)
af <- cor.test(analysis_10weekday_baseline$Entropy, analysis_10weekday_baseline$sum)
ag <- cor.test(analysis_10weekday_baseline$NormalizedEntropy, analysis_10weekday_baseline$sum)
ah <- cor.test(analysis_10weekday_baseline$HomeStay, analysis_10weekday_baseline$sum)

Baseline <- c(aa$estimate[[1]], ab$estimate[[1]], ac$estimate[[1]], ad$estimate[[1]], ae$estimate[[1]], af$estimate[[1]], ag$estimate[[1]], ah$estimate[[1]])

ba <- cor.test(analysis_10weekday_followup$LocationVariance, analysis_10weekday_followup$sum)
bb <- cor.test(analysis_10weekday_followup$SpeedMean, analysis_10weekday_followup$sum)
bc <- cor.test(analysis_10weekday_followup$SpeedVariance, analysis_10weekday_followup$sum)
bd <- cor.test(analysis_10weekday_followup$TotalDistance, analysis_10weekday_followup$sum)
be <- cor.test(analysis_10weekday_followup$NumberofClusters, analysis_10weekday_followup$sum)
bf <- cor.test(analysis_10weekday_followup$Entropy, analysis_10weekday_followup$sum)
bg <- cor.test(analysis_10weekday_followup$NormalizedEntropy, analysis_10weekday_followup$sum)
bh <- cor.test(analysis_10weekday_followup$HomeStay, analysis_10weekday_followup$sum)

Followup <- c(ba$estimate[[1]], bb$estimate[[1]], bc$estimate[[1]], bd$estimate[[1]], be$estimate[[1]], bf$estimate[[1]], bg$estimate[[1]], bh$estimate[[1]])

ca <- cor.test(analysis_10weekday_change$LocationVariance, analysis_10weekday_change$minus)
cb <- cor.test(analysis_10weekday_change$SpeedMean, analysis_10weekday_change$minus)
cc <- cor.test(analysis_10weekday_change$SpeedVariance, analysis_10weekday_change$minus)
cd <- cor.test(analysis_10weekday_change$TotalDistance, analysis_10weekday_change$minus)
ce <- cor.test(analysis_10weekday_change$NumberofClusters, analysis_10weekday_change$minus)
cf <- cor.test(analysis_10weekday_change$Entropy, analysis_10weekday_change$minus)
cg <- cor.test(analysis_10weekday_change$NormalizedEntropy, analysis_10weekday_change$minus)
ch <- cor.test(analysis_10weekday_change$HomeStay, analysis_10weekday_change$minus)

change <- c(ca$estimate[[1]], cb$estimate[[1]], cc$estimate[[1]], cd$estimate[[1]], ce$estimate[[1]], cf$estimate[[1]], cg$estimate[[1]], ch$estimate[[1]])

Feature <- c("Location_Variance", "Speed_Mean", "Speed_Variance", "Total_Distance", "Number_of_Cluster", "Entropy", "Normalized_Entropy", "Home_Stay")

analysis_10weekday_total <- cbind(Feature)

analysis_10weekday_total <- cbind(analysis_10weekday_total, Baseline = round(Baseline,digits = 2), Followup = round(Followup,digits = 2), Change = round(change, digits = 2))

analysis_10weekday_total

```




# 2. weekend
```{r features_Location Variance, message=FALSE, warning=FALSE}
getwd()
setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekend")

library(readr)

gps_dir <- c("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekend")
gps_file <- list.files(gps_dir)
gps_file_count <- length(gps_file)

# import dataset, gps sensing file
for(i in 1:gps_file_count){
    oname <- substr(gps_file[i], 1,13)
    assign(oname, read_csv(paste(gps_dir,"/", gps_file[i], sep = "")))
}

# Location Variance calculate function
location_variance <- function(x){
    latitude_var = var(x$latitude, na.rm = T)
    longitude_var = var(x$longitude, na.rm = T)
    location_variance = log10(latitude_var + longitude_var)
    return(location_variance)
}

features_10weekend_all <- data.frame()

# feature_10week_all <- features data set

for(i in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[i], sep = ""))
    cc <-location_variance(df)
    features_10weekend_all <- rbind(features_10weekend_all, c(cc))
}

names(features_10weekend_all) <- c("LocationVariance")

################################################################################

uid <- substr(list.files(gps_dir), 11, 13)
uid <- as.data.frame(uid)
features_10weekend_all <- cbind(features_10weekend_all, uid)
features_10weekend_all <- features_10weekend_all[,c(2,1)]

# cbind the "uid" to features_10weekend_all dataset.

################################################################################

## Speed Mean, Speed Variance, Total Distance calculate.
user_speed <- data.frame()

for(j in 1:gps_file_count){
    x <- read_csv(paste(gps_dir,"/", gps_file[j], sep = ""))
    k <- nrow(x) - 1
    
    u00_stat <- data.frame()
    
    for(i in 2:k){
        v = sqrt(((x[[i,5]]-x[[i-1,5]]) / (x[[i,1]] - x[[i-1,1]]))^2 + ((x[[i,6]]-x[[i-1,6]]) / (x[[i,1]] - x[[i-1,1]]))^2)
        
        distance = sqrt((x[[i,5]]-x[[i-1,5]])^2 + (x[[i,6]]-x[[i-1,6]])^2)
        
        u00_stat <- rbind(u00_stat, c(v, distance))
    }
    colnames(u00_stat) <- c("V", "distance")
    user_speed <- rbind(user_speed, c(mean(u00_stat$V), var(u00_stat$V), sum(u00_stat$distance)))
}



features_10weekend_all <- cbind(features_10weekend_all, user_speed)

names(features_10weekend_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance")


```

```{r clustering and features about Number of Clusters, message=FALSE, warning=FALSE}

# Number of location clusters found by the adaptive k-means algorithm
install.packages("akmeans", repos="http://cran.rstudio.com/")
library(akmeans)

set.seed(212)

num_cluster <- function(x){
    n_stationary <- subset(x, travelstate == "stationary")
    set.seed(212)
    adaptive_kmeans <- akmeans(n_stationary[,c("latitude", "longitude")],ths1 = 0.0000085, min.k =1, max.k = 100)
    return(nrow(adaptive_kmeans$centers))
}


numberCluster <- data.frame()


for(i in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[i], sep = ""))
    cc <- num_cluster(df)
    numberCluster <- rbind(numberCluster, cc)
}

features_10weekend_all <- cbind(features_10weekend_all, numberCluster)

names(features_10weekend_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters")


```

### Feature_Cluster_entropy calculate code
```{r features about Entropy, message=FALSE, warning=FALSE}


cluster_entropy <- function(x){
    x_stationary <- subset(x, travelstate == "stationary")
    set.seed(212)
    adaptive_kmeans <- akmeans(x_stationary[,c("latitude", "longitude")],ths1 = 0.0000085, min.k =1, max.k = 10)
    return(adaptive_kmeans$size)
}

Entropy <- data.frame()

for(j in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[j], sep = ""))
    aa <- cluster_entropy(df)
    aa <- prop.table(aa)
    
    k <- features_10weekend_all[[j,6]]
    x = 0
    for(i in 1:k){
        hap <- aa[i] * log(aa[i])
        x = x + hap
    }
    
    Entropy <- rbind(Entropy, -x)
}

features_10weekend_all <- cbind(features_10weekend_all, Entropy)

names(features_10weekend_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters", "Entropy")

```

### Feature_Normalized Entropy calculate code
```{r Normalized Entropy}

norm_entropy = features_10weekend_all$Entropy / log(features_10weekend_all$NumberofClusters)

norm_entropy <- as.data.frame(norm_entropy)
norm_entropy$norm_entropy[is.na(norm_entropy$norm_entropy)] <- 0

features_10weekend_all <- cbind(features_10weekend_all, norm_entropy)

names(features_10weekend_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters", "Entropy", "NormalizedEntropy")


```

### Feature_Home Stay calculate code
Actually, it is difficult to definite home cluster. so i just determined that the biggest size of cluster is home cluster. so, there will be a little mistake with real home cluster.

```{r features about Home Stay, message=FALSE, warning=FALSE}
homestay <- function(x){
    set.seed(212)
    adaptive_kmeans <- akmeans(x[,c("latitude", "longitude")],ths1 = 0.0000085, min.k=1)
    return(adaptive_kmeans$size)
}

Homestay <- data.frame()

for(i in 1:gps_file_count){
    df <- read_csv(paste(gps_dir,"/", gps_file[i], sep = ""))
    aa <- cluster_entropy(df)
    aa <- prop.table(aa)
    
    home_sort <- sort(aa, decreasing = TRUE)[1]
    
    Homestay <- rbind(Homestay, home_sort)
}

features_10weekend_all <- cbind(features_10weekend_all, Homestay)

names(features_10weekend_all) <- c("uid", "LocationVariance", "SpeedMean", "SpeedVariance", "TotalDistance", "NumberofClusters", "Entropy", "NormalizedEntropy", "HomeStay")

```


```{r}

####################### 완성된 featurers를 통한 분석 비교 #######################


analysis_10weekend_baseline <- merge(x = features_10weekend_all, y = phq9_ans_baseline, by ="uid")
analysis_10weekend_followup <- merge(x = features_10weekend_all, y = phq9_ans_followup, by ="uid")
analysis_10weekend_change <- merge(x = features_10weekend_all, y = phq9_ans_change, by ="uid")


aa <- cor.test(analysis_10weekend_baseline$LocationVariance, analysis_10weekend_baseline$sum)
ab <- cor.test(analysis_10weekend_baseline$SpeedMean, analysis_10weekend_baseline$sum)
ac <- cor.test(analysis_10weekend_baseline$SpeedVariance, analysis_10weekend_baseline$sum)
ad <- cor.test(analysis_10weekend_baseline$TotalDistance, analysis_10weekend_baseline$sum)
ae <- cor.test(analysis_10weekend_baseline$NumberofClusters, analysis_10weekend_baseline$sum)
af <- cor.test(analysis_10weekend_baseline$Entropy, analysis_10weekend_baseline$sum)
ag <- cor.test(analysis_10weekend_baseline$NormalizedEntropy, analysis_10weekend_baseline$sum)
ah <- cor.test(analysis_10weekend_baseline$HomeStay, analysis_10weekend_baseline$sum)

Baseline <- c(aa$estimate[[1]], ab$estimate[[1]], ac$estimate[[1]], ad$estimate[[1]], ae$estimate[[1]], af$estimate[[1]], ag$estimate[[1]], ah$estimate[[1]])

ba <- cor.test(analysis_10weekend_followup$LocationVariance, analysis_10weekend_followup$sum)
bb <- cor.test(analysis_10weekend_followup$SpeedMean, analysis_10weekend_followup$sum)
bc <- cor.test(analysis_10weekend_followup$SpeedVariance, analysis_10weekend_followup$sum)
bd <- cor.test(analysis_10weekend_followup$TotalDistance, analysis_10weekend_followup$sum)
be <- cor.test(analysis_10weekend_followup$NumberofClusters, analysis_10weekend_followup$sum)
bf <- cor.test(analysis_10weekend_followup$Entropy, analysis_10weekend_followup$sum)
bg <- cor.test(analysis_10weekend_followup$NormalizedEntropy, analysis_10weekend_followup$sum)
bh <- cor.test(analysis_10weekend_followup$HomeStay, analysis_10weekend_followup$sum)

Followup <- c(ba$estimate[[1]], bb$estimate[[1]], bc$estimate[[1]], bd$estimate[[1]], be$estimate[[1]], bf$estimate[[1]], bg$estimate[[1]], bh$estimate[[1]])

ca <- cor.test(analysis_10weekend_change$LocationVariance, analysis_10weekend_change$minus)
cb <- cor.test(analysis_10weekend_change$SpeedMean, analysis_10weekend_change$minus)
cc <- cor.test(analysis_10weekend_change$SpeedVariance, analysis_10weekend_change$minus)
cd <- cor.test(analysis_10weekend_change$TotalDistance, analysis_10weekend_change$minus)
ce <- cor.test(analysis_10weekend_change$NumberofClusters, analysis_10weekend_change$minus)
cf <- cor.test(analysis_10weekend_change$Entropy, analysis_10weekend_change$minus)
cg <- cor.test(analysis_10weekend_change$NormalizedEntropy, analysis_10weekend_change$minus)
ch <- cor.test(analysis_10weekend_change$HomeStay, analysis_10weekend_change$minus)

change <- c(ca$estimate[[1]], cb$estimate[[1]], cc$estimate[[1]], cd$estimate[[1]], ce$estimate[[1]], cf$estimate[[1]], cg$estimate[[1]], ch$estimate[[1]])

Feature <- c("Location_Variance", "Speed_Mean", "Speed_Variance", "Total_Distance", "Number_of_Cluster", "Entropy", "Normalized_Entropy", "Home_Stay")

analysis_10weekend_total <- cbind(Feature)

analysis_10weekend_total <- cbind(analysis_10weekend_total, Baseline = round(Baseline,digits = 2), Followup = round(Followup,digits = 2), Change = round(change, digits = 2))

analysis_10weekend_total

```






```{r, eval=FALSE, include=FALSE}

#json file
install.packages("jsonlite")
library(jsonlite)
setwd("C:/Users/Lee Min Hyung/Downloads/dataset.tar/dataset/dataset/EMA")
data = fromJSON("EMA_definition.json")
data=data.frame(data)

#unix time convert
as.Date(as.POSIXct(u00$time, origin="1970-01-01"))

u00$time <- as.Date(as.POSIXct(u00$time, origin="1970-01-01"))
u01$time <- as.Date(as.POSIXct(u01$time, origin="1970-01-01"))

## 요일 반환
install.packages("lubridate")
library(lubridate)
Sys.setlocale("LC_TIME", "C")

wday(as.Date(as.POSIXct(1367999097, origin="1970-01-01")))
# Sunday: 1 ~ Saturday: 7


#############################
# try.... fail
for(i in gps_dir){
i[1] <<-as.Date(as.POSIXct(i[1], origin="1970-01-01"))
}


#############################
#try.... fail

for(i in gps_3_variance){
    location_variance(i)
}

for(i in gps_3_variance){
write.csv(i, file = paste(gps_dir,"/", gps_3_variance[i]), append = TRUE, quote = FALSE, sep = "")
}
############################


## k-means

test_gps_u00 <- subset(gps_u00, travelstate == "stationary")

test <- kmeans(test_gps_u00[,c("latitude", "longitude")], 1)
test8<- kmeans(test_gps_u00[,c("latitude", "longitude")], 8)


####################### k-means... optimize k find #######################

install.packages("NbClust")
library(NbClust)


## NbClust packages
nc <- NbClust(training.data, min.nc=2, max.nc=15, method="kmeans")
par(mfrow=c(1,1))
barplot(table(nc$Best.n[1,]),
 xlab="Numer of Clusters", ylab="Number of Criteria",
 main="Number of Clusters Chosen")

## some of squares
wssplot <- function(data, nc=15, seed=212){
  wss <- (nrow(data)-1)*sum(apply(data,2,var))
  for (i in 2:nc){
    set.seed(seed)
    wss[i] <- sum(kmeans(data, centers=i)$withinss)}
  plot(1:nc, wss, type="b", xlab="Number of Clusters",
       ylab="Within groups sum of squares")}

wssplot(training.data)

####################### 완성된 featurers를 통한 분석 비교 #######################
setwd("C:/Users/Lee Min Hyung/Desktop/data")
curious <- read.csv("features_10week_all.csv")
bb <- phq9_ans_followup
names(bb) <- c("id")
ab <- merge(x = curious, y = bb, by="id")
ab <- ab[c(1,2,3,4,5,6,7,8,9,10,11,12,13,23)]
cor.test(ab$NumberofClusters, ab$NA.10)

################################################################################

# 연습...
aa <- features_10week_all
bb <- phq9_ans_baseline
ab <- merge(x = aa, y = bb, by="uid")
ab <- ab[c(1,2,3,4,5,16)]

ab_lm <- lm(sum ~ LocationVariance, data = ab)
summary(ab_lm)
cor.test(ab$TotalDistance, ab$sum)


aa <- features_10week_all
bb <- phq9_ans_followup
ab <- merge(x = aa, y = bb, by="uid")
ab <- ab[c(1,2,3,4,5,6,17)]
cor.test(ab$NumberofCluster, ab$sum)

 -> -0.4376051


```



```{r, eval=FALSE, include=FALSE}
head(as.Date(as.POSIXct(gps_u00$time, origin="1970-01-01")))



gps_week10_dir <- c("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps")
gps_week10_file <- list.files(gps_week10_dir)




weekday_cc <- data.frame()
weekend_cc <- data.frame()


todate <- function(x){
    x$date <- as.Date(as.POSIXct(x$time, origin="1970-01-01"))
}


setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekday")

for(i in 1: gps_file_count){
    setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekday")
    df <- read_csv(paste("weekday10_",substr(gps_file[i], 5,7), ".csv",sep = ""))
    df$date <- as.Date(as.POSIXct(df$time, origin="1970-01-01"))
}


{
weekday_1 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-03-27" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-03-28" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-03-29" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-01" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-02" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-03" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-04" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-05")
    return(assign(paste(y,"_1"), y))
}


weekday_2 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-01" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-02" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-03" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-04" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-05" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-08" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-09" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-10" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-11" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-12")
    return(assign(paste(y,"_2"), y))
}

weekday_3 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-08" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-09" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-10" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-11" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-12" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-15" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-16" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-17" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-18" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-19")
    return(assign(paste(y,"_3"), y))
}

weekday_4 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-15" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-16" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-17" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-18" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-19" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-22" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-23" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-24" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-25" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-26")
    return(assign(paste(y,"_4"), y))
}

weekday_5 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-22" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-23" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-24" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-25" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-26" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-29" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-30" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-01" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-02" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-03")
    return(assign(paste(y,"_5"), y))
}

weekday_6 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-29" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-30" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-01" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-02" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-03" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-06" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-07" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-08" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-09" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-10")
    return(assign(paste(y,"_6"), y))
}

weekday_7 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-06" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-07" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-08" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-09" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-10" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-13" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-14" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-15" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-16" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-17")
    return(assign(paste(y,"_7"), y))
}

weekday_8 <- function(x,y){
    y <- subset(x, as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-13" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-14" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-15" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-16" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-17" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-20" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-21" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-22" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-23" | as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-24")
    return(assign(paste(y,"_8"), y))
}
}





for(i in 1:gps_file_count){
    plz <- read_csv(paste"C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week2_gps/weekday", "/weekday10_",substr(gps_file[i], 5,7),".csv", sep = ""))
    
    pname <- paste("weekday2_",substr(gps_file[i], 5,7),sep = "")
    weekday_1(plz, pname)
    weekday_2(plz, pname)
    weekday_3(plz, pname)
    weekday_4(plz, pname)
    weekday_5(plz, pname)
    weekday_6(plz, pname)
    weekday_7(plz, pname)
    weekday_8(plz, pname)
}


    write.csv(weekday_split(plz, pname), paste("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week2_gps/weekday", "/weekday2_",substr(gps_file[i], 5,7),".csv", sep = ""), row.names = FALSE)


for(i in 1:gps_file_count){
    plz <- read_csv(paste(gps_dir,"/", gps_file[i], sep = ""))
    
    oname <- paste("weekend10_",substr(gps_file[i], 5,7), sep = "")
    assign(oname, weekend_split(plz, oname))
    write.csv(weekend_split(plz, oname), paste("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week2_gps/weekend", "/weekend10_",substr(gps_file[i], 5,7),".csv", sep = ""), row.names = FALSE)
    
    pname <- paste("weekday10_",substr(gps_file[i], 5,7), sep = "")
    assign(pname, weekday_split(plz, pname))
    write.csv(weekday_split(plz, pname), paste("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week2_gps/weekday", "/weekday10_",substr(gps_file[i], 5,7),".csv", sep = ""), row.names = FALSE)
}

weekday_split <- function(x,y){
    y <- subset(x, wday(as.Date(as.POSIXct(x$time, origin="1970-01-01"))) >= 2 & wday(as.Date(as.POSIXct(x$time, origin="1970-01-01"))) <= 6)
    return(y)
}


for(i in 1:gps_file_count){
    oname <- paste("weekend10_",substr(gps_file[i], 5,7), sep = "")
    assign(oname, subset)




weekday10_u59$date <- as.Date(as.POSIXct(weekday10_u59$time, origin="1970-01-01"))




setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekday")

for(i in 1:gps_file_count){
  setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekday")
    df <- read_csv(paste("weekday10_",substr(gps_file[i], 5,7), ".csv",sep = ""))
    weekday_cc <- rbind(weekday_cc, weekday2_func(df))
}  

for(i in 1:gps_file_count){
  setwd("C:/Users/Lee Min Hyung/Desktop/dataset.tar/dataset/dataset/sensing/week10_gps/weekend")
    df2 <- read_csv(paste("weekend10_",substr(gps_file[i], 5,7), ".csv",sep = ""))
    weekend_cc <- rbind(weekend_cc, weekend2_func(df2))
}


oname <- paste("weekend10_",substr(gps_file[i], 5,7), sep = "")




weekday2_func <- function(x){
    cc <- c(which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-03-27")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-01")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-08")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-15")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-22")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-29")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-06")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-13")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-20")[1],
    
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-27")[1])
    return(cc)
}


weekend2_func <- function(x){
    cc <- c(which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-03-30")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-06")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-13")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-20")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-27")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-04")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-11")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-18")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-25")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-06-01")[1])
    return(cc)
}






{
cc <<- weekday2_func(weekday10_u00)

    small <- paste("weekday10_", substr(gps_file[32], 11,13),sep = "")
    assign(paste(small,"_1", sep = ""), weekday10_u00[cc[1]:cc[3]-1,])
    assign(paste(small,"_2", sep = ""), weekday10_u39[cc[2]:cc[4]-1,])
    assign(paste(small,"_3", sep = ""), weekday10_u39[cc[3]:cc[5]-1,])
    assign(paste(small,"_4", sep = ""), weekday10_u39[cc[4]:cc[6]-1,])
    assign(paste(small,"_5", sep = ""), weekday10_u39[cc[5]:cc[7]-1,])
    assign(paste(small,"_6", sep = ""), weekday10_u39[cc[6]:cc[8]-1,])
    assign(paste(small,"_7", sep = ""), weekday10_u39[cc[7]:cc[9]-1,])
    assign(paste(small,"_8", sep = ""), weekday10_u39[cc[8]:cc[10]-1,])
}
    
    


weekend2_func <- function(x){
    cc <- c(which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-03-30")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-06")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-13")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-20")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-04-27")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-04")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-11")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-18")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-05-25")[1],
    which(as.Date(as.POSIXct(x$time, origin="1970-01-01")) == "2013-06-01")[1])
    return(cc)
}




cc <<- weekend2_func(weekend10_u00)



weekend2_assign <- function(x){
    cc <<- weekend2_func(x)
    small <- paste("weekend10_", substr(gps_file[1], 11,13),sep = "")
        
    assign(paste(small,"_1", sep = ""), x[cc[1]:cc[3]-1,])
    assign(paste(small,"_2", sep = ""), x[cc[2]:cc[4]-1,])
    assign(paste(small,"_3", sep = ""), x[cc[3]:cc[5]-1,])
    assign(paste(small,"_4", sep = ""), x[cc[4]:cc[6]-1,])
    assign(paste(small,"_5", sep = ""), x[cc[5]:cc[7]-1,])
    assign(paste(small,"_6", sep = ""), x[cc[6]:cc[8]-1,])
    assign(paste(small,"_7", sep = ""), x[cc[7]:cc[9]-1,])
    assign(paste(small,"_8", sep = ""), x[cc[8]:cc[10]-1,])
}

weekend2_assign(weekend10_u00)




for(j in 1:9){
        oname <- df[c(weekday2_func(df)[j]:weekday2_func(df)[j+1]),]
        pname <- df[c(weekend2_func(df2)[j]:weekend2_func(df2)[j+1]),]
    }
```



```{r clustering, eval=FALSE, include=FALSE}

# calculate two points with latitude and longitude

d_long = longitude_2 - longitude_1
d_lat = latitude_2 - latitude_1

a = sin(d_lat/2) * sin(d_lat/2) + cos(latitude_1) * cos(latitude_2) * sin(d_long/2) * sin(d_long/2)

c = 2 * atan(sqrt(a)/sqrt(1-a))

d = r * c

r = 지구의 반지름 = 6371km
 -> in the clustering, threshold is 0.5km
 clusters centroid & farthest point distance should be lower than 0.5km
 so, calculate d, and compare.
 #######################################################################

distance_twodot <- function(lat_1, long_1, lat_2, long_2){
    d_lat = lat_2 - lat_1
    d_long = long_2 - long_1
    
    a = sin(d_lat/2) * sin(d_lat/2) + cos(lat_1) * cos(lat_2) * sin(d_long/2) * sin(d_long/2)
    c = 2 * atan(sqrt(a)/sqrt(1-a))
    r = 6371
    
    d = r * c
    
    return(d)
}



```


```{r, eval=FALSE, include=FALSE}
# k-Means clustering


# test_gps_u00 <- subset(gps_u00, travelstate == "stationary")

# test <- kmeans(test_gps_u00[,c("latitude", "longitude")], 1)
# test8<- kmeans(test_gps_u00[,c("latitude", "longitude")], 8)


# leader_cluster
# leader <- leaderCluster(points, radius = 0.5,  weights = rep(1, nrow(pointa)), max_iter = 10L, distance = c("Lp", "L1", "L2", "Linf", "haversine"), p = 2)



# install.packages("leaderCluster")
# library(leaderCluster)

# leader <- leaderCluster(test_gps_u00[,c("latitude", "longitude")], radius = 0.5, max_iter = 10L, distance = "Lp")

# leader <- leaderCluster(test_gps_u51[,c("latitude", "longitude")], radius = 0.5, max_iter = 30L, distance = "Lp")

#################################################################################
```

